Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning

### 2016-11-25 paper.tex
Removing some references of MKL

 %structured sparsity regularizers \cite{Micchelli2010,Micchelli2013}.
The problem of searching for a combinations of basic kernels can be rephrased as a regularization problem in which the prediction function is the sum of functions $f_r$ in the RKHS of kernel $\KK_r$ and the regularization term is the combination of the norms of the $f_r$ in the associated RKHS \cite{Micchelli2005a}. %,Micchelli2007
For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.

>>>>

 %structured sparsity regularizers \cite{Micchelli2010,Micchelli2013}.
%The problem of searching for a combinations of basic kernels can be rephrased as a regularization problem in which the prediction function is the sum of functions $f_r$ in the RKHS of kernel $\KK_r$ and the regularization term is the combination of the norms of the $f_r$ in the associated RKHS \cite{Micchelli2005a}. %,Micchelli2007
%For example if $q=1$ this is a parametric version of the group Lasso \cite{Meier2009}, see e.g. \cite{Maurer2012}.
